\frb: Very Large Array Burst Properties and Implications for Overall FRB Population

### 2016-11-16 repeater-vladata.tex
new event rate figure

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{lombscargle}
\caption{Lomb-Scargle periodogram.
\label{fig:ls}}
\end{center}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{lombscargle}
\caption{Lomb-Scargle periodogram with 95\% limit on power from last observing campaign
\label{fig:ls}}
\end{center}
\end{figure}

Bursts seem to drop throughout last campaign. The nominal rate is 1e-4 per second, but a someone higher rate is inferred from modeling shown in Figure \ref{fig:rate}.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{event_rate_contours}
\caption{Rate versus rate change during last campaign.
\label{fig:rate}}
\end{center}
\end{figure}
